---
title: "Experimental conditions"
author: "Ana M. Palacio"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: yes
html_document:
    code_folding: hide
    fig_height: 6
    fig_width: 6
    df_print: paged
    toc: yes
    toc_float: yes
bibliography: packages.bib
nocite: '@*'
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

# General project set-up 

```{r libraries, results="hide"}

# Load all libraries and sources required to run the script
    library(tidyverse)
    library(ggthemes)
    library(ggplot2)
    library(plyr)
    library(tidyr)

    library(plotrix)
    library(lme4)
    library(lmerTest)
    library(emmeans)
    library(reshape2)

# Graphs
# Plots
MyTheme<-theme_bw() +  
theme(legend.position="top",
          plot.background=element_blank(),
          #axis.text.x = element_text(angle = 90, vjust = 0.5),
          panel.grid.major.y = element_blank(),
          panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.grid.minor.y = element_blank(),
          legend.box.background = element_rect(),
          legend.title = element_blank(),
          panel.background =element_rect(fill = NA, 
                                         color = "black"))

# Treatment colors
Treat_fill<-scale_fill_manual(values =
                           c("#2b83ba", "#003399",
                             "#d7191c", "#660000"))

Treat_colour<-scale_colour_manual(values =
                           c("#2b83ba", "#003399",
                             "#d7191c", "#660000"))
  
```

# 1. Temperature

```{r}
# Data
    Temp<-read.csv("Data/Temperature.csv", header = TRUE)
    #summary(Temp)
    Temp$Time<-as.POSIXct(Temp$Time, format="%m/%d/%Y %H:%M",
                               tz = "America/New_York" )
    Temp<-Temp %>% filter(!between(Time, as.POSIXct('2023-05-18 08:50:00.00'),
                                as.POSIXct('2023-05-18 09:55:00.00')))
   
    
    Temp <- gather(Temp, Tank, Temperature, 
                   Tank.1:Tank.8, factor_key=TRUE)
    #Temp<-Temp[Temp$Tank!="Tank.6",]
    #Temp<-Temp[Temp$Tank!="Tank.7",]
    Temp<-Temp %>% mutate(Group =
                     case_when(Tank == "Tank.1" ~ "Control Temperature", 
                               Tank == "Tank.2" ~ "High Temperature", 
                               Tank == "Tank.3" ~ "High Temperature", 
                               Tank == "Tank.4" ~ "Control Temperature",
                               Tank == "Tank.5" ~ "Control Temperature", 
                               Tank == "Tank.6" ~ "Donor colonies", 
                               Tank == "Tank.7" ~ "Donor colonies", 
                               Tank == "Tank.8" ~ "High Temperature"))
    Temp$Group<-factor(Temp$Group, levels = c("Control Temperature",
                                              "High Temperature",
                                              "Donor colonies"))
    
    Temp<-Temp %>% mutate(Group2 =
                     case_when(Group == "Control Temperature" ~ "28 C", 
                               Group == "High Temperature" ~ "31 C", 
                               Group == "Donor colonies" ~ "Donor colonies"))
    
    # Remove data from tank that had a sensor failed
    Temp<-Temp %>% filter((Time<as.POSIXct('2023-06-02 00:50:00.00') | 
                          Tank!="Tank.8"))
    Temp$Date<-as.Date(Temp$Time)
    Temp$Day<-as.numeric(difftime(Temp$Date, 
                                  as.Date("2023-05-01"), units="days"))
    summary(Temp)
```

Temperature conditions during the whole experiment 

```{r}
Temp_summary <- ddply (Temp[Temp$Day>0, ], .(Group2),
                         summarise,
                meanT = mean (Temperature, na.rm = T), 
                sdT = sd (Temperature, na.rm = T), 
                seT = std.error (Temperature, na.rm = T))
Temp_summary
```

Temperature conditions excluding ramp-up days

```{r}
Temp_summary <- ddply (Temp[Temp$Day>5, ], .(Group2),
                         summarise,
                meanT = mean (Temperature, na.rm = T), 
                sdT = sd (Temperature, na.rm = T), 
                seT = std.error (Temperature, na.rm = T))
Temp_summary
```


### Plot temperature by tanks

Raw values

```{r}
Temperature<- ggplot(Temp, aes (Time, Temperature)) +
  geom_jitter(aes(colour=Group), alpha=1, size=0.5)+
  # stat_summary(fun.data = "mean_cl_boot", 
  #              geom = "errorbar", width = 0.2,  color="black" )+
  # stat_summary(fun=mean, geom="point",  color="black") + 

  theme(legend.position = "bottom")+
  scale_y_continuous(limits = c(26, 32),
                      breaks = seq(0,32, 2),  
                      #   expand = c(0.01, 0.01),
                      name=("Temperature (C)")) +
  
    scale_x_datetime(breaks = "7 days",
                      date_labels = "%b %d",
                      limits = c(as.POSIXct("2023-05-02 12:30"),
                                 as.POSIXct("2023-06-24 18:00")),
                      #  expand = c(0.01, 0.01),
                      name=("Date")) +
   
  geom_vline(xintercept = as.POSIXct("2023-05-18"),
              linetype=2)+
  annotate("text", x = c(as.POSIXct("2023-05-13"), as.POSIXct("2023-06-12")), y = 27, label = "*")+
  
  MyTheme + facet_wrap(~Tank, ncol = 4)+
  #facet_wrap(~(fct_rev(Tank)), ncol = 4)+
  scale_colour_manual(
  values = c("#2b83ba", "#d7191c", "gray"))+
  theme(legend.position = "none")

#Temperature
```

Daily mean values by tank

```{r}
Temperature<- ggplot(Temp, aes (Day, Temperature, colour=Group2)) +
  #geom_jitter(aes(colour=Group), alpha=1, size=0.5)+
  stat_summary(fun.data = "mean_cl_boot", 
                geom = "errorbar", width = 0.2)+
  stat_summary(fun=mean, geom="line", alpha=0.8) + 

  theme(legend.position = "bottom")+
  scale_y_continuous(limits = c(27.3, 31.3),
                      breaks = seq(0,32, 1),  
                      #   expand = c(0.01, 0.01),
                      name=expression(Temperature~(degree~C))) +
  scale_x_continuous(breaks = seq(0, 51, 7),
                      name=("Days in the experiment")) +
  
    # scale_x_date(breaks = "7 days",
    #                   date_labels = "%b %d",
    #                   limits = c(as.Date("2023-05-02"),
    #                              as.Date("2023-06-12")),
    #                   #  expand = c(0.01, 0.01),
    #                   name=("Date")) +
   
  #geom_vline(xintercept = as.Date(c("2023-05-18", "2023-06-02")),
  #            linetype=2, alpha=0.5)+
  # annotate("text", x = c(as.Date("2023-05-13"), 
  #                        as.Date("2023-06-02")), y = 27.5, label = "*")+
  geom_vline(xintercept = c(17, 32),
              linetype=2, alpha=0.5)+
  
  MyTheme + facet_wrap(~Tank, ncol = 4)+
  #facet_wrap(~(fct_rev(Tank)), ncol = 4)+
  scale_colour_manual(
  values = c("#2b83ba", "#d7191c", "gray"))+
  theme(legend.position = "top")

Temperature

#ggsave(file="Outputs/Temperature.svg", plot=Temperature, width=8, height=4)
```

Daily mean values by treatment and experimental timeline

```{r}
TimeLine<- ggplot(Temp, aes (Day, Temperature, 
                                colour=Group2)) +
  #geom_jitter(aes(colour=Group), alpha=1, size=0.5)+
  stat_summary(fun.data = "mean_cl_boot", 
                geom = "errorbar", width = 0.2)+
  stat_summary(fun=mean, geom="line", alpha=0.8) + 

  theme(legend.position = "bottom")+
  scale_y_continuous(limits = c(27.3, 31.3),
                      breaks = seq(0,32, 1),  
                      #   expand = c(0.01, 0.01),
                      name=expression(Temperature~(degree~C))) +
  scale_x_continuous(breaks = seq(0, 51, 8),
                      name=("Days in the experiment")) +
  annotate("text", x = c(14, 31), y = 27.5, label = "*")+
  geom_vline(xintercept = c(1, 17, 32),
              linetype=2, alpha=0.5)+
  
  MyTheme + facet_wrap(~Group2, ncol = 1)+
  scale_colour_manual(
  values = c("#2b83ba", "#d7191c", "gray"))+
  theme(legend.position = "top")

#TimeLine

#ggsave(file="Outputs/TimeLine.svg", plot=TimeLine, width=4, height=6)
```

```{r}
TimeLine2<- ggplot(Temp[Temp$Group!="Donor colonies", ], 
                   aes (Day, Temperature, 
                                colour=Group2)) +
  stat_summary(fun.data = "mean_cl_boot", 
                geom = "errorbar", width = 0.2)+
  stat_summary(fun=mean, geom="line", alpha=0.8) + 

  scale_y_continuous(limits = c(27.5, 31.1),
                      breaks = seq(0,32, 0.5),  
                      #   expand = c(0.01, 0.01),
                      name=expression(Temperature~(degree~C))) +
  scale_x_continuous(breaks = seq(0, 51, 8),
                      name=("Days in the experiment")) +
  annotate("text", x = c(14, 31), y = 29, label = "*")+
  geom_vline(xintercept = c(1, 32),
              linetype=2, alpha=0.5)+
  
  MyTheme + 
  scale_colour_manual(
  values = c("#2b83ba", "#d7191c"))+
  theme(legend.position = "top")
TimeLine2

#ggsave(file="Outputs/TimeLine.svg", plot=TimeLine2, width=4, height=6)
```

# 2. Nutrients

```{r}
# Data
    data<-read.csv("Data/Nutrients.csv", header = TRUE)
    #summary(data)
    data$N<-as.numeric(data$N)
    data$Date<-as.Date(data$Date)
    
    library(lubridate)
    data$Week<-isoweek(ymd(data$Date))
    data$Week<-as.numeric(data$Week-17)
    
    data$Target<-factor(data$Target,
                           levels=c("0", "5", "6"))
    # data$Pump<-factor(data$Pump,
    #                        levels=c("1", "2"))
    
    data<-droplevels(data)
    data$Treatment<-factor(data$Treatment, 
                           levels = c ("LN_28", "LN_31", "HN_28", "HN_31",
                                       "Healthy", "Disease",  "Stock", "VAT"))
    data$Treatment3<-factor(paste(data$Nutrients, 
                                  data$Disease, sep = "_"))
    data<-data[data$Date!="2023-05-18", ]
    data$Day<-as.numeric(difftime(data$Date, 
                                  as.Date("2023-05-01"), units="days"))

    summary(data)
```

## Exploratory plots

```{r}
NH4_plot<- ggplot(data, aes (Target, NH4)) +
  #geom_boxplot ()+
  geom_jitter(aes(colour=Arm, shape=Pump), alpha=1)+
  # stat_summary(fun.data = "mean_cl_boot", 
  #              geom = "errorbar", width = 0.2,  color="black" )+
  # stat_summary(fun=mean, geom="point",  color="black") + 
  #geom_point(shape=21)+

 
  theme(legend.position = "bottom")+
  scale_y_continuous(#limits = c(0, 11),
                      breaks = seq(0,12, 2.5),  
                      #   expand = c(0.01, 0.01),
                      name=("NH4 [umol/L]")) +
  # geom_hline(yintercept = 4.1, linetype=2)+
  # geom_hline(yintercept = 0.3, linetype=2)+
  MyTheme +
  facet_grid(Beaker.conditions~Date, scales = "free_y")

#NH4_plot
```


```{r}
NH4_genotype<- ggplot(data, aes (Date, NH4)) +
  geom_boxplot ()+
  geom_jitter(aes(colour=Genotype, shape=Arm), alpha=1)+
  # stat_summary(fun.data = "mean_cl_boot", 
  #              geom = "errorbar", width = 0.2,  color="black" )+
  # stat_summary(fun=mean, geom="point",  color="black") + 
  #geom_point(shape=21)+

  theme(legend.position = "bottom")+
  scale_y_continuous(limits = c(0, 12),
                      breaks = seq(0,10, 1),  
                      #   expand = c(0.01, 0.01),
                      name=("NH4 [umol/L]")) +
  # geom_hline(yintercept = 4.1, linetype=2)+
  # geom_hline(yintercept = 0.3, linetype=2)+
  MyTheme +
  facet_wrap(Disease~Nutrients, scales = "free_y")
#NH4_genotype
```

```{r}
NH4_Arms<- ggplot(data, aes (Day, NH4)) +
  #geom_boxplot ()+
  geom_jitter(aes(colour=Arm, shape=Beaker.conditions), alpha=1)+
  stat_summary(fun.data = "mean_cl_boot", 
                geom = "errorbar", width = 0.2,  color="black" )+
   stat_summary(fun=mean, geom="point",  color="black") + 
  #geom_point(shape=21)+

  theme(legend.position = "bottom")+
  geom_vline(xintercept = c(17, 32),
              linetype=2, alpha=0.5)+
  scale_x_continuous(limits = c(0, 55),
                      breaks = seq(0,55, 7),  
                      #   expand = c(0.01, 0.01),
                      name=("Days in the experiment")) +
  scale_y_continuous(limits = c(0, 15),
                      breaks = seq(0,20, 1),  
                      #   expand = c(0.01, 0.01),
                      name=("NH4 [umol/L]")) +
  # geom_hline(yintercept = 4.1, linetype=2)+
  # geom_hline(yintercept = 0.3, linetype=2)+
  MyTheme +
  facet_wrap(Disease~Nutrients)

#NH4_Arms
```

Remove VAT and stock solution values 

```{r}
NH4_Temp<- ggplot(data, aes (Day, NH4, fill=Treatment, 
                               colour=Treatment,
                               shape=Beaker.conditions)) +
 
  #geom_jitter(aes(colour=Treatment, shape=Beaker.conditions), 
  #alpha=1, size =1)+
  #geom_boxplot ()+
  scale_shape_manual(values=c(21, 22))+
  scale_color_manual(values=c("#2b83ba", "#d7191c", "#003399", "#660000",
                              '#CC9900','#FF33FF', '#FF6600', "#999999"))+
  scale_fill_manual(values=c("#2b83ba", "#d7191c", "#003399", "#660000",
                              '#CC9900','#FF33FF', '#FF6600', "#999999"))+
  # stat_summary(fun.data = "mean_cl_boot", 
  #               geom = "errorbar", width = 0.2)+
  stat_summary(fun.data = "mean_cl_boot", 
                geom = "line")+
  stat_summary(fun=mean, geom="point") + 
  #geom_point(shape=21)+
   geom_vline(xintercept = c(17, 32),
              linetype=2, alpha=0.5)+
  scale_x_continuous(limits = c(0, 55),
                      breaks = seq(0,55, 7),  
                      #   expand = c(0.01, 0.01),
                      name=("Day in the experiment")) +
  scale_y_continuous(#limits = c(0, 60),
                      breaks = seq(0, 20, 2),  
                      #   expand = c(0.01, 0.01),
                      name=("NH4 [umol/L]")) +
  # geom_hline(yintercept = 4.1, linetype=2)+
  # geom_hline(yintercept = 0.3, linetype=2)+
  #ylim()+
  MyTheme
  #NH4_Temp+facet_wrap(~Nutrients)
NH4_Temp+facet_grid(Disease~Nutrients)
```


```{r}
NH4_W<- ggplot(data, aes (Week, NH4, fill=Treatment, colour=Treatment)) +
 
  geom_jitter(aes(colour=Treatment, shape=Beaker.conditions), 
              alpha=1, size =1)+
  geom_boxplot(aes (Week, NH4, fill=Treatment, group=Week))+
  scale_shape_manual(values=c(21, 22))+
  scale_color_manual(values=c("#2b83ba", "#d7191c", "#003399", "#660000",
                              '#CC9900','#FF33FF', '#FF6600', "#999999"))+
  scale_fill_manual(values=c("#2b83ba", "#d7191c", "#003399", "#660000",
                              '#CC9900','#FF33FF', '#FF6600', "#999999"))+
  stat_summary(fun.data = "mean_cl_boot", 
                geom = "errorbar", width = 0.2)+
  stat_summary(fun.data = "mean_cl_boot", 
                geom = "line")+
  stat_summary(fun=mean, geom="point") + 
  #geom_point(shape=21)+
 
  theme(legend.position = "bottom")+
  scale_y_continuous(limits = c(0, 20),
                      breaks = seq(0,20, 1),  
                      #   expand = c(0.01, 0.01),
                      name=("NH4 [umol/L]")) +
  # geom_hline(yintercept = 4.1, linetype=2)+
  # geom_hline(yintercept = 0.3, linetype=2)+
  MyTheme
  #NH4_Temp+facet_wrap(~Nutrients)
  NH4_W+facet_grid(Disease~Nutrients)
```

Remove Stock solution, VAT and donnor tank samples 

```{r}
Corals<-data[data$Nutrients!="Other", ]

Concentrations <- ddply (Corals, .(Treatment, Disease, Beaker.conditions, Nutrients, Day), summarise,
                meanNH4 = mean (NH4, na.rm = T), 
                sdNH4 = sd (NH4, na.rm = T), 
                seNH4 = std.error (NH4, na.rm = T))
#Concentrations

Concentrations$Beaker.conditions<-factor(Concentrations$Beaker.conditions, 
                                            levels=c("Coral", "Blank"))
Concentrations$Nutrients<-factor(Concentrations$Nutrients, 
                                            levels=c("LN", "HN"))

write.csv(Concentrations, "Outputs/Concentrations.csv")

# Standard error of the mean

NH4_day<-ggplot(Concentrations, 
                aes(x=Day, y=(meanNH4), shape=Beaker.conditions, 
                                    colour=Treatment)) + 
    geom_errorbar(aes(ymin=(meanNH4-seNH4), ymax=(meanNH4+seNH4)), 
                  width=.1, position=position_dodge(0.5)) +
    geom_line(position=position_dodge(0.5)) +
    geom_point(position=position_dodge(0.5), aes(fill=Treatment), size=1)+
    scale_shape_manual(values=c(21, 22))+
    scale_color_manual(values=c("#2b83ba", "#d7191c", "#003399", "#660000"))+
    scale_fill_manual(values=c("#2b83ba", "#d7191c", "#003399", "#660000"))+
    geom_vline(xintercept = c(32),
                linetype=2, alpha=0.5)+
    scale_x_continuous(#limits = c(0, 55),
                        breaks = seq(0,55, 8),  
                        #   expand = c(0.01, 0.01),
                        name=("Days in the experiment")) +
    scale_y_continuous(#limits = c(0, 60),
                        breaks = seq(0, 35, 2.5),  
                      #   expand = c(0.01, 0.01),
                      name=("NH4 [uM]")) + MyTheme +
  facet_grid(Nutrients~Disease)
NH4_day

#ggsave(file="Outputs/Nutrients.svg", plot=NH4_day, width=7.5, height=5)
```

Remove empty beakers

```{r}
Concentrations2 <- ddply (Corals[Corals$Beaker.conditions=="Coral", ],
                          .(Treatment, Nutrients, Day),
                         summarise,
                meanNH4 = mean (NH4, na.rm = T), 
                sdNH4 = sd (NH4, na.rm = T), 
                seNH4 = std.error (NH4, na.rm = T))
#Concentrations2

Concentrations2$Nutrients<-factor(Concentrations2$Nutrients, 
                                            levels=c("LN", "HN"))

# Standard error of the mean

NH4_day<-ggplot(Concentrations2, 
                aes(x=Day, y=(meanNH4), 
                                    colour=Treatment)) + 
    geom_errorbar(aes(ymin=(meanNH4-seNH4), ymax=(meanNH4+seNH4)), 
                  width=.1, position=position_dodge(0.5)) +
    geom_line(position=position_dodge(0.5)) +
    geom_point(position=position_dodge(0.5), aes(fill=Treatment), size=1)+
    scale_shape_manual(values=c(21, 22))+
    scale_color_manual(values=c("#2b83ba", "#d7191c", "#003399", "#660000"))+
    scale_fill_manual(values=c("#2b83ba", "#d7191c", "#003399", "#660000"))+
    geom_vline(xintercept = c(1, 32),
                linetype=2, alpha=0.5)+
    scale_x_continuous(#limits = c(0, 55),
                        breaks = seq(0,55, 8),  
                        #   expand = c(0.01, 0.01),
                        name=("Days in the experiment")) +
    scale_y_continuous(#limits = c(0, 60),
                        breaks = seq(0, 20, 2),  
                      #   expand = c(0.01, 0.01),
                      name=("NH4 [uM]")) + MyTheme #+
  #facet_grid(~Disease)
NH4_day
```

# Figure: Experimental conditions 

```{r}
library(gridExtra)
experiment<-grid.arrange(TimeLine2, NH4_day, ncol = 2)
experiment

#ggsave(file="Outputs/Experiment_conditions.svg", plot=experiment, width=8.5, height=4)
```

## Other figures 

```{r}
NH4_by_coral<- ggplot(Corals[Corals$Beaker.conditions=="Coral", ],
                 aes (Day, NH4, fill=Treatment, 
                               colour=Treatment)) +
 
  geom_jitter(aes(colour=Treatment, shape=Beaker.conditions), 
              alpha=1, size =0.5)+
  scale_shape_manual(values=c(21, 22))+
  scale_color_manual(values=c("#2b83ba", "#d7191c", "#003399", "#660000"))+
  scale_fill_manual(values=c("#2b83ba", "#d7191c", "#003399", "#660000"))+
  # stat_summary(fun.data = "mean_cl_boot", 
  #               geom = "errorbar", width = 0.2)+
  stat_summary(fun.data = "mean_cl_boot", 
                geom = "line")+
  stat_summary(fun=mean, geom="point") + 
  #geom_point(shape=21)+
   geom_vline(xintercept = c(17, 32),
              linetype=2, alpha=0.5)+
  scale_x_continuous(limits = c(0, 55),
                      breaks = seq(0,55, 7),  
                      #   expand = c(0.01, 0.01),
                      name=("Day in the experiment")) +
  scale_y_continuous(limits = c(0, 60),
                      breaks = seq(0, 60, 5),  
                      #   expand = c(0.01, 0.01),
                      name=("NH4 [umol/L]")) +
  MyTheme
#NH4_Temp+facet_wrap(~Nutrients)
NH4_by_coral+facet_grid(Disease~Nutrients)
```

```{r}
Concentrations <- ddply (data, .(Nutrients, Disease, Date),
                         summarise,
                meanNH4 = mean (NH4, na.rm = T), 
                sdNH4 = sd (NH4, na.rm = T))
#Concentrations

Concentrations<-Concentrations %>% 
                mutate_if(is.numeric, round, digits=2)

```

```{r}

Concentrations_Day_Beaker <- ddply (data, .(Nutrients, Day, Beaker.conditions),
                         summarise,
                meanNH4 = mean (NH4, na.rm = T), 
                sdNH4 = sd (NH4, na.rm = T))
Concentrations_Day_Beaker

Concentrations_Nutrients_Day <- ddply (data, .(Nutrients, Day),
                         summarise,
                meanNH4 = mean (NH4, na.rm = T), 
                sdNH4 = sd (NH4, na.rm = T))
Concentrations_Nutrients_Day

Concentrations_Nutrients_Week <- ddply (data, .(Nutrients, Week),
                         summarise,
                meanNH4 = mean (NH4, na.rm = T), 
                sdNH4 = sd (NH4, na.rm = T))
Concentrations_Nutrients_Week

Concentrations<-Concentrations %>% 
 mutate_if(is.numeric, round, digits=2)

# write.csv(Concentrations, "Outputs/weekly_NH4.csv", row.names = F)
```

#3. Treatment effects on NH4 concentrations

```{r}
## model 1: LMER for both species
  fit1<-lmerTest::lmer(NH4 ~Nutrients * Temp * Disease * Week +
                         (1|Beaker.conditions), data=data[data$Nutrients!="Other", ])
  isSingular(fit1)
  anova(fit1)
  step(fit1)
  ranova(fit1)
  
  summary(fit1)
  par(mfrow=c(2,2))
  plot(fit1)
  par(mfrow=c(1,1))
```

```{r}
#Pairwise comparisons
Sw.emmc<-multcomp::cld(emmeans(fit1, specs=c("Nutrients", "Disease")))
Sw.emmc
```

# Packages used

```{r}
# Creates bibliography 
#knitr::write_bib(c(.packages()), "packages.bib")
```
