---
title: "Ofav Symbiodiniaceae community under environmental Co-factors"
author: "Ana Palacio-Castro"
date: "`r Sys.Date()`"
always_allow_html: yes
output:
  pdf_document:
    toc: yes
  html_document:
    code_folding: hide
    fig_height: 8
    fig_width: 8
    df_print: paged
    toc: yes
    toc_float: yes
  word_document:
    toc: yes
bibliography: packages.bib
nocite: '@*'
editor_options:
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# 1. Libraries and project set-up:

```{r libraries}
  library(tidyverse) # install.packages('tidyverse')
  #library(devtools)  # install.packages("devtools")
  #devtools::install_github("jrcunning/steponeR")
  #install.packages("rlang")
  library(steponeR)
  library(plyr)
  library(dplyr)
  library(reshape2)
  library(ggplot2)
  library(ggpubr)

  library(lmerTest)
  library(emmeans)
  library(effects)
  library(modelsummary) # model results in table
  # library(lsmeans) #cld functon 
  #library(jtools) # Plot modesl
  library(kableExtra) # ANOVA tables

MyTheme<-theme_bw() +  
theme(legend.position="top",
          plot.background=element_blank(),
          #axis.text.x = element_text(angle = 90, vjust = 0.5),
          panel.grid.major.y = element_blank(),
          panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.grid.minor.y = element_blank(),
          legend.box.background = element_rect(),
          legend.title = element_blank(),
          panel.background =element_rect(fill = NA, 
                                         color = "black"))#

Fill.colour<-c ("#2b83ba", "#003399", "#d7191c", "#660000")

Treat_colour<-scale_colour_manual(values =
                           c("#2b83ba", "#003399",
                             "#d7191c", "#660000"))
```


# 2. Calculate qPCR RATIOS fo all the samples  

```{r CalculateRatios, include=FALSE}

# Get the list of files with qPCR data
Plates <- list.files(path="Data", pattern=".csv", full.names=T)
Plates

# Run the steponeR program to get the S/H cell ratios
  # This needs to follow your plate target labels, otherwise it will not work

Ofav.Out <- steponeR(files=Plates, target.ratios=c("A.Ofav", "B.Ofav", "D.Ofav"), 
                     fluor.norm=list(A=0, B=0, D=0, Ofav=0),
                     copy.number=list(A=1, B=1, D=3, Ofav=1),
                     ploidy=list(A=1, B=1, D=1, Ofav=2),
                     extract=list(A=0.813, B=0.813, D=0.813, Ofav=0.982))

# Target ratio results
Ofav<-Ofav.Out$result
```

## 2.1. Data CLEANING A

```{r DataCleaning}
  # 1. Check and remove NTC wells
    ntc <- Ofav[which(Ofav$Sample.Name=="NTC"), ]
    Ofav <- droplevels(Ofav[!rownames(Ofav) %in% rownames(ntc), ])
    
  # 2. Check and remove + Control wells
    Positive <- Ofav[which(Ofav$Sample.Name=="+"), ]
    Ofav <- droplevels(Ofav[!rownames(Ofav) %in% rownames(Positive), ])

  # 3.If Clade only detected in one technical replicate, set its ratio to NA and make them =0
    One.A<- Ofav[which(Ofav$A.reps==1),]
    Ofav$A.Ofav[which(Ofav$A.reps==1)] <- NA
    
    One.B<- Ofav[which(Ofav$B.reps==1),]
    Ofav$B.Ofav[which(Ofav$B.reps==1)] <- NA
    
    One.D<- Ofav[which(Ofav$D.reps==1),]
    Ofav$D.Ofav[which(Ofav$D.reps==1)] <- NA
    
    Ofav$A.Ofav[is.na(Ofav$A.Ofav)] <- 0
    Ofav$B.Ofav[is.na(Ofav$B.Ofav)] <- 0
    Ofav$D.Ofav[is.na(Ofav$D.Ofav)] <- 0
```

## 2.2. Get the total S/H cell ratios and log 10 transformations

```{r}
  # Total SH
    Ofav$TotalSH<-(Ofav$A.Ofav + Ofav$B.Ofav+ Ofav$D.Ofav)
    
  # Log 10
        Ofav$logA.SH <- log10(Ofav$A.Ofav)
        Ofav$logB.SH <- log10(Ofav$B.Ofav)
        Ofav$logD.SH <- log10(Ofav$D.Ofav)
        Ofav$logSH<-log10(Ofav$TotalSH)
        
        Ofav$logA.SH[which(Ofav$A.Ofav==0)] <- NA
        Ofav$logB.SH[which(Ofav$B.Ofav==0)] <- NA
        Ofav$logD.SH[which(Ofav$D.Ofav==0)] <- NA
        Ofav$logSH[which(Ofav$TotalSH==0)] <- NA
  
```    

## 2.3. Import the sample information

```{r Samples}
# Get the sample information for your qPCR plates (if you use a template)
  SampleName<-read.csv("Metadata/Sample_Plates.csv")
  SampleName <- SampleName[!(is.na(SampleName$Sample.ID)), ]
  SampleName <- SampleName[SampleName$Fragment!="Acropora", ]
  SampleName<-SampleName[, -(12:37)]
  
# Get the sample metadata (treatments, data points, etc)
  Metadata<-read.csv("Metadata/Fragment_Replicate.csv")

# Get the disease outcome information
  Disease<-read.csv("Metadata/SCTLD_mortality.csv")
  Disease<-select(Disease, Disease_Status, Fragment, Start_Of_Lesion)

  #Sample.duplicates <-SampleName[duplicated(SampleName$Sample.Plate),] 
  
# 3. Create unique sample ID+FileName to relabel samples  
  Ofav$Sample.Plate<-paste(Ofav$Sample.Name, Ofav$File.Name, sep = "_" )
  head(SampleName)
  head(Ofav)
   
# Replace Sample.Names in qPCR data - Different for each project
rownames(SampleName) <- SampleName$Sample.Plate
    Ofav$TP<-SampleName[as.character(Ofav$Sample.Plate), "TP"]
    Ofav$Status<-SampleName[as.character(Ofav$Sample.Plate), "Status"]
    Ofav$Date<-SampleName[as.character(Ofav$Sample.Plate), "Date"]
    Ofav$Date<-as.Date(Ofav$Date, format="%Y-%m-%d")
    Ofav$Fragment<-SampleName[as.character(Ofav$Sample.Plate), "Fragment"]
    Ofav$Sample.ID<-SampleName[as.character(Ofav$Sample.Plate), "Sample.ID"]
    
# Get treatment information
  Ofav<-left_join(Ofav, Metadata, by="Fragment")

# Creates a unique ID for a core-sampling time 
  Ofav$Sample<-paste(Ofav$Fragment, Ofav$TP, Ofav$Status, sep='_')
  
# Remove non experimental corals
  Donors <- Ofav[is.na(Ofav$Nutrients), ]
  Ofav <- droplevels(Ofav[!rownames(Ofav) %in% rownames(Donors), ])

# Environmental
  Ofav$N_T<-paste(Ofav$Nutrients, as.character(Ofav$Temp), sep="_")
  
# Disease information
   Ofav<-left_join(Ofav, Disease, by="Fragment")
  Ofav <- Ofav[Ofav$TP!="T3", ]
  
  Lession_T2<-select(Ofav, Fragment, Disease_Status)
  Lession_T2<- unique(Lession_T2)
  colnames(Lession_T2)<-(c("Fragment", "Status_T2"))
  Ofav<-left_join(Ofav, Lession_T2, by="Fragment")
  Ofav$Status_T2<-Ofav$Status_T2 %>% replace_na("ND")
```

## 2.4. Data CLEANING B

```{r DataCleaningB}

# 5. Remove (-) control
    #NegControl <- Ofav[which(Ofav$Sample=="NA_NA"), ]
    #Ofav <- droplevels(Ofav[!rownames(Ofav) %in% rownames(NegControl), ])

# 6.If coral detected in one technical replicate, remove the sample
    ReRun.Coral <- Ofav[which(Ofav$Ofav.reps==1), ]
    Ofav <- droplevels(Ofav[!rownames(Ofav) %in% rownames(ReRun.Coral), ])
    
    NoHSratio <- Ofav[which(Ofav$TotalSH==0), ]
    Ofav <- droplevels(Ofav[!rownames(Ofav) %in% rownames(NoHSratio), ])
    
# 7. High ST    
    StDe1.5 <- Ofav[which((Ofav$Ofav.CT.sd>1.5)|(Ofav$D.CT.sd>1.5)), ]
    Ofav <- droplevels(Ofav[!rownames(Ofav) %in% rownames(StDe1.5), ])
  
# 8.Suspiciously late coral amplification
    # Histo_Ofav_CT<-qplot(Ofav.CT.mean, data=Ofav, binwidth=0.15)
    # Histo_Ofav_CT 
  
  LateCoral<-Ofav[which(Ofav$Ofav.CT.mean>22), ]
  Ofav <- droplevels(Ofav[!rownames(Ofav) %in% rownames(LateCoral), ])
    
  # Samples to Re-run    
  ToRe_Run1<-rbind(ReRun.Coral, NoHSratio)
  ToRe_Run1<-rbind(ToRe_Run1, ReRun.Coral)   
  ToRe_Run1<-rbind(ToRe_Run1, StDe1.5)
  ToRe_Run1<-rbind(ToRe_Run1, LateCoral)
  ToRe_Run1<-ToRe_Run1 %>% distinct()
```
  
## 2.5. Chose bw samples ran more than once

```{r remove duplicates}

 ReRunA <- Ofav[duplicated(Ofav$Sample),] 
  n_RunA <- data.frame(table(Ofav$Sample))
  colnames(n_RunA)<-c("Sample","RanA")
  Ofav<-join(Ofav, n_RunA, type = "left")
# 
  DuplicatesA <- Ofav[(Ofav$RanA>1),]
  # write.csv(DuplicatesA, "DuplicatesA.csv")

Duplicates<-ggplot(DuplicatesA, aes(Date, logSH, colour=factor(File.Name))) +
 stat_summary(fun=mean, geom="line") +
  geom_point() 
Duplicates
```

##2.6. Remove duplicates

```{r remove duplicates2}
#List of dupilcates to remove  
ToRem1<-read.csv("ToRemove.csv")
Ofav<-Ofav[!(Ofav$Sample.Plate %in% ToRem1$Sample.Plate),]
# 
# # Check for replicates again--should have none
  n_RunB <- data.frame(table(Ofav$Sample))
  colnames(n_RunB)<-c("Sample","RanB")
  Ofav<-join(Ofav, n_RunB, type = "left")

# 
# # List of dupplicated samples, should have 0 rows now -->
   DuplicatesB <- Ofav[(Ofav$RanB>1),]
# # write.csv(DuplicatesB, file = 'DuplicatesB.csv')
```

```{r DProp, include=FALSE}

# Clade Proportion
  # D Proportion
  Ofav$D.Prp<-(Ofav$D.Ofav/Ofav$TotalSH)
  Ofav$A.Prp<-(Ofav$A.Ofav/Ofav$TotalSH)
  Ofav$B.Prp<-(Ofav$B.Ofav/Ofav$TotalSH)
  
  hist(Ofav$D.Prp)
  hist(Ofav$A.Prp)
  hist(Ofav$B.Prp)
  
  Ofav$D.per<-(Ofav$D.Prp*100)
  Ofav$A.per<-(Ofav$A.Prp*100)
  Ofav$B.per<-(Ofav$B.Prp*100)
```
  
## 3. Exploratory plots

## Samples before disease inoculation

```{r}
# Order factors
  Ofav$N_T<-factor(Ofav$N_T, levels = c("LN_28", "HN_28", "LN_31", "HN_31"))
  
# Initial data
  T1<-Ofav[Ofav$TP=="T1", ]
  T1<-T1[T1$Sample!="D_868_T1_AH", ]
  T1$RanA<-NULL
  T1$RanB<-NULL
```

```{r}
Dprop_Hist_T1 <- ggplot(T1, aes (D.Prp, fill=as.factor(N_T))) +
      geom_histogram(binwidth = 0.01) + 
      scale_x_continuous(name= expression(Proportion~of~italic(Durusdinium~trenchii)),
                         breaks=seq(0, 1, 0.01)) +
      scale_y_continuous(name= expression(Number~of~italic(O.faveolata)~fragments),
                         breaks=seq(0, 90, 10)) +
      theme(plot.background=element_blank(),
                         panel.grid.major.y = element_blank(),
                         panel.grid.major.x = element_blank(),
            legend.position=c(0.2,0.8),
                            legend.box.background = element_rect(), 
            panel.background =element_rect(fill = NA, color = "black")) +
      scale_fill_manual(values=Fill.colour,
                    name = "Treatment"# , 
                    #labels=c("C dominated", "D dominated")
                    )
Dprop_Hist_T1 + facet_grid(~Disease)

Aprop_Hist_T1 <- ggplot(T1, aes (A.Prp, fill=as.factor(Genotype))) +
      geom_histogram(binwidth = 0.01) + facet_wrap(~Nutrients) + 
      scale_x_continuous(name= expression(Proportion~of~italic(Durusdinium~trenchii)),
                         breaks=seq(0, 1, 0.01)) +
      scale_y_continuous(name= expression(Number~of~italic(O.faveolata)~fragments),
                         breaks=seq(0, 90, 10)) +
      theme(plot.background=element_blank(),
                         panel.grid.major.y = element_blank(),
                         panel.grid.major.x = element_blank(),
            legend.position=c(0.2,0.8),
                            legend.box.background = element_rect(), 
            panel.background =element_rect(fill = NA, color = "black"))
Aprop_Hist_T1 + facet_grid(Nutrients~Disease)
```

# 4. Final plots and stats 

## 4.1 Symbiont to host cell ratio

```{r}
S_H_T1 <- ggplot(T1[T1$Disease=="SCTLD", ],
                 aes (x=Genotype, y=TotalSH, fill=as.factor(N_T))) +
     #geom_point(aes(fill=N_T, shape=Genotype), position=position_dodge(width=0.6), alpha=0.5)+
     stat_summary(fun.data = "mean_cl_boot", aes(fill=as.factor(N_T)),
                  linewidth = 1, size = 1, shape=21, alpha=0.8, 
                  position=position_dodge(width=0.6))+
      #scale_y_log10() +
     scale_y_continuous(#breaks=seq(0, 1, 0.002),
                        name=expression(log[10]~(S/H)~cell~ratio)) +
     theme(plot.background=element_blank(),
                         panel.grid.major.y = element_blank(),
                         panel.grid.major.x = element_blank(),
          legend.position="bottom",
                            legend.box.background = element_rect(), 
          panel.background =element_rect(fill = NA, color = "black")) +
    scale_fill_manual(values=Fill.colour,
                    #labels=c("C dominated", "D dominated")
                    name = "Treatment")+
    scale_shape_manual(values=c(23, 21, 24),
                      #labels=c("Control", "SCTLD"),
                      name = "Transmission")+
    guides(fill=guide_legend(override.aes = list(shape=21)))
S_H_T1

S_H_T1 <- ggplot(T1[T1$Disease=="SCTLD", ],
                 aes (x=N_T, y=TotalSH, fill=as.factor(N_T))) +
     geom_point(aes(colour=N_T, shape=Genotype), position=position_dodge(width=0.6), 
                alpha=0.5)+
     stat_summary(fun.data = "mean_cl_boot", aes(fill=as.factor(N_T)),
                  linewidth = 1, size = 1, shape=21, alpha=0.8, 
                  position=position_dodge(width=0.6))+
     Treat_colour+ 
     scale_y_continuous(breaks=seq(0.05, 0.25, 0.05),
                        name="Relative symbiont abundance (S/H cell ratio)") +
     theme(plot.background=element_blank(),
                         panel.grid.major.y = element_blank(),
                         panel.grid.major.x = element_blank(),
          legend.position="bottom",
                            legend.box.background = element_rect(), 
          panel.background =element_rect(fill = NA, color = "black")) +
    scale_fill_manual(values=Fill.colour,
                    #labels=c("C dominated", "D dominated")
                    name = "Treatment")+
    scale_shape_manual(values=c(23, 25, 24),
                      labels=c("A", "B", "C"),
                      name = "Colony")+
    guides(fill=guide_legend(override.aes = list(shape=21)))
S_H_T1
```

S/H model

```{r}
LM_SH_0 <- lmer(logSH ~ Nutrients + Temp +
                             (1|Colony), REML=TRUE, data=T1[T1$Disease=="SCTLD", ])
  step(LM_SH_0)
  anova(LM_SH_0)
  #summary(LM_SH_0)
  ranova(LM_SH_0)

LM_SH_1 <- lmer(logSH ~ Nutrients + (1 | Colony), REML=TRUE,
                data=T1[T1$Disease=="SCTLD", ])
  step(LM_SH_1)
  summary(LM_SH_1)
  anova(LM_SH_1)

# ANOVAs
    # Convert ANOVA results into dataframes allows for easier name manipulation
    av.LM_SH_0 <- data.frame (anova(LM_SH_0))
    av.LM_SH_1 <- data.frame (anova(LM_SH_1))
    
    # Putting all into one dataframe/table
    anova_SH <- data.frame(cbind
                    (c("Nutrients", "Temperature"), 
                         rbind(av.LM_SH_0))) 
    colnames(anova_SH) <- c("", "Sum Sq", "Mean Sq", "N Df" , "D Df",
                                     "F value", "Pr(>F)")
    row.names(anova_SH) <- NULL

    # create HTML table using kableExtra
    anova_SH %>% kable("html", digits=4,  caption = 'S/H cell ratio model') %>% 
    kable_styling(bootstrap_options = "striped", full_width = F)

# Model summary  
  SH_models<-list("Initial" = LM_SH_0, 
                   "Final" = LM_SH_1)
  modelsummary(SH_models, stars = TRUE, 
             #statistic = c('std.error', 'p.value', 'conf.int'),
             title = 'S/H cell ratio model outputs')
  
# Mean values
  SH_Colony_summary <- T1 %>%
    dplyr::group_by(Genotype) %>%
    dplyr::summarise(
      MeanSH = mean(TotalSH, na.rm = T),
      SD = sd(TotalSH, na.rm = T))
  SH_Colony_summary
  #write.csv(SH_Colony_summary, "Outputs/SH_Colony.csv")
  
  SH_nutrients_summary <- T1 %>%
    dplyr::group_by(Nutrients) %>%
    dplyr::summarise(
      MeanSH = mean(TotalSH, na.rm = T),
      SD = sd(TotalSH, na.rm = T))
  SH_nutrients_summary
  #write.csv(SH_nutrients_summary, "Outputs/SH_Nutrients.csv")
```


## 4.2 *Durusdinium* relative abundance

```{r}
Dprop_T1 <- ggplot(T1[T1$Disease=="SCTLD", ],
                   aes (x=Genotype, y=D.Prp*100, fill=as.factor(N_T))) +
    geom_point(aes(fill=N_T, shape=Status_T2), position=position_dodge(width=0.6))+
    scale_y_continuous(name=italic(Durusdinium)~"(%)",
                         breaks=seq(0, 100, 0.2),
                         limits = c(99.1, 100)) +
    stat_summary(fun.data = "mean_cl_boot", aes(fill=as.factor(N_T)),
                   linewidth = 1, size = 1,alpha=0.8, 
                   shape=21,position=position_dodge(width=0.6))+
    theme(plot.background=element_blank(),
                         panel.grid.major.y = element_blank(),
                         panel.grid.major.x = element_blank(),
                         legend.position="bottom",
                         legend.box.background = element_rect(), 
                         panel.background =element_rect(fill = NA, color = "black")) +
      scale_fill_manual(values=Fill.colour,
                    name = "Treatment"# , 
                    #labels=c("C dominated", "D dominated")
                    )+
      scale_shape_manual(values=c(23, 21, 24),
                      #labels=c("Control", "SCTLD"),
                      name = "Lession")+
      guides(fill=guide_legend(override.aes = list(shape=21)))
#Dprop_T1

Dprop_T1 <- ggplot(T1[T1$Disease=="SCTLD", ],
                   aes (x=N_T, y=D.Prp*100, fill=as.factor(N_T))) +
    geom_point(aes(colour=N_T, shape=Colony), 
               position=position_dodge(width=0.6), alpha=0.5)+
    scale_y_continuous(name=italic(Durusdinium)~"(%)",
                         breaks=seq(0, 100, 0.2),
                         limits = c(99.1, 100)) +
    stat_summary(fun.data = "mean_cl_boot", aes(fill=as.factor(N_T)),
                   linewidth = 1, size = 1,alpha=0.8, 
                   shape=21,position=position_dodge(width=0.6))+
    theme(plot.background=element_blank(),
                         panel.grid.major.y = element_blank(),
                         panel.grid.major.x = element_blank(),
                         legend.position="bottom",
                         legend.box.background = element_rect(), 
                         panel.background =element_rect(fill = NA, color = "black")) +
      scale_fill_manual(values=Fill.colour, name = "Treatment")+
      Treat_colour+ 
      scale_shape_manual(values=c(23, 25, 24),
                      #labels=c("Control", "SCTLD"),
                      name = "Lession")+
      guides(fill=guide_legend(override.aes = list(shape=21)))
Dprop_T1
```

*Durusdinium* models 

```{r}
# Fit a binomial regression model
BM_DP <- glm(D.Prp ~ Nutrients + Temp, 
               family="binomial", data=Ofav)
    anova(BM_DP)
    summary(BM_DP)
    #plot(BM_DP)
    step(BM_DP)
    
LM_DP  <- lmer(D.Prp ~ Nutrients + Temp + (1|Colony), data=Ofav)
    anova(LM_DP)
    ranova(LM_DP)
    summary(LM_DP)
    #plot(LM_DP)
    step(LM_DP)

# Multicomp
D.p_Emm<-multcomp::cld(emmeans(LM_DP, specs = c("Temp", "Nutrients")))
  D.p_Emm
  #write.csv(D.p_Emm, "Outputs/Dpr_Emmeans.csv")
```

```{r}
Aprop_T1 <- ggplot(T1[T1$Disease=="SCTLD", ],
                   aes (x=Genotype, y=A.Prp*100, fill=as.factor(N_T))) +
    geom_point(aes(fill=N_T, shape=Status_T2), position=position_dodge(width=0.6))+
    scale_y_continuous(name=italic(Symbiodinium)~"(%)",
                         limits = c(0, 0.9),
                         breaks=seq(0, 100, 0.2)) +
    stat_summary(fun.data = "mean_cl_boot", aes(fill=as.factor(N_T)),
                   linewidth = 1, size = 1, alpha=0.8, 
                   shape=21, position=position_dodge(width=0.6))+
    theme(plot.background=element_blank(),
          panel.grid.major.y = element_blank(),
          panel.grid.major.x = element_blank(),
          legend.position="bottom",
          legend.box.background = element_rect(), 
          panel.background =element_rect(fill = NA, color = "black")) +
    scale_fill_manual(values=Fill.colour,
                    name = "Treatment"# , 
                    #labels=c("C dominated", "D dominated")
                    )+
    scale_shape_manual(values=c(23, 21, 24),
                      #labels=c("Control", "SCTLD"),
                      name = "Lession")+
    guides(fill=guide_legend(override.aes = list(shape=21)))
Aprop_T1

Aprop_T1 <- ggplot(T1[T1$Disease=="SCTLD", ],
                   aes (x=N_T, y=A.Prp*100, fill=as.factor(N_T))) +
    geom_jitter(aes(colour=N_T, shape=Genotype), position=position_dodge(width=0.6),
                alpha=0.5)+
    scale_y_continuous(name=italic(Symbiodinium)~"(%)",
                         limits = c(0, 0.9),
                         breaks=seq(0, 100, 0.2)) +
    stat_summary(fun.data = "mean_cl_boot", aes(fill=as.factor(N_T)),
                   linewidth = 1, size = 1, alpha=0.8, 
                   shape=21, position=position_dodge(width=0.6))+
    theme(plot.background=element_blank(),
          panel.grid.major.y = element_blank(),
          panel.grid.major.x = element_blank(),
          legend.position="bottom",
          legend.box.background = element_rect(), 
          panel.background =element_rect(fill = NA, color = "black")) +
    scale_fill_manual(values=Fill.colour,
                    name = "Treatment"# , 
                    #labels=c("C dominated", "D dominated")
                    )+
   Treat_colour+ 
    scale_shape_manual(values=c(23, 25, 24),
                      #labels=c("Control", "SCTLD"),
                      name = "Lession")+
    guides(fill=guide_legend(override.aes = list(shape=21)))
Aprop_T1

LM_AP  <- lmer(A.Prp ~ Nutrients + Temp + (1|Colony), data=Ofav)
    anova(LM_AP)
    ranova(LM_AP)
    summary(LM_AP)
    #plot(LM_AP)
    step(LM_AP)

A.p_Emm<-multcomp::cld(emmeans(LM_AP, specs = c("Temp", "Nutrients")))
A.p_Emm
#write.csv(A.p_Emm, "Outputs/Apr_Emmeans.csv")
```

```{r}
Figure5 <- ggarrange(S_H_T1, ggarrange(Dprop_T1 + theme(legend.position = "none"), 
                                       Aprop_T1+ theme(legend.position = "none"),
                                       nrow = 2), ncol = 2)
Figure5
#ggsave("Outputs/Figure5.svg", Figure5, width=7, height=5,dpi = 300)
```

# Packages used

```{r}
# Creates bibliography 
#knitr::write_bib(c(.packages()), "packages.bib")
```